mime-version: 1.0
content-type: text/plain; charset=ISO-8859-1
content-transfer-encoding: 8bit
subject: Your new OnionMail

onionmail: !
onion: !
username: !
pop3password: !
sha1: !
smtppassword: !
nick: !
MsgSize: !
MaxMsgXuser: !
MsgOld: !
Scrambler: Default
vmatmail: !
vmatpass: !
inetaddr: !
					
This is your new OnionMail address:
%onionmail%

To use this you must connect via Tor to the server:
%onion%

To read your email messages:
POP3 Server %onion% port 110
Use STARTTLS and plain password.
The POP3 usename is:
%username%
And the password is:
%pop3password%

To send your messages:
SMTP Server %onion% port 25
Use STARTTLS and plain password.
The SMTP username is:
%username%
And the password is:
%smtppassword%

Your VMAT address is:
%vmatmail%

The VMAT password is:
%vmatpass%

Your address in Intenret and in the TOR network can appear:
%inetaddr%

The maximum message size is: %MsgSize% bytes.
Number maximum messages in your inbox: %MaxMsgXuser%.
The messages will delete after %MsgOld% days.
This PGP message is encrypted with %Scrambler% algorithm.

Don't forget to check the SSL certificate SHA-1 hash when 
you connect first time. The SHA-1 is:
%sha1%

Retry to connect after you accept the SSL certificate.

To get more informations about the server send a message
to the server mail address server@%onion% 
with subject IDENT.

To get more help and informations about rules and term of
use send a message to the server mail address server@%onion%
with subject RULEZ. 

Remember to create now your PGP key and use PGP.
When you create a your PGP key don' t forget to get the exit node list
via the EXIT LIST message to the server. Please create some alternative id
like <username.%onion%@exitdomain.tld> 
to communicate correctly with internet users.

%nick% server at %onion% 
